Estimation of the road traffic sound levels in urban areas based on non-negative matrix factorization techniques

### 2018-01-11 paper/gloaguenNmfTraffic.tex
abstract is here

\title{Estimation of the road traffic sound levels based on Non-Negative Matrix Factorization}

@@

>>>>

\title{Estimation of the road traffic sound levels in urban areas based on non-negative matrix factorization techniques}

@@

The advent of low cost acoustic monitoring devices raises new interesting approaches for improving the monitoring the acoustic quality of urban areas. Assuming that transportation is the major source of annoyance, state of the art approaches consider as input an estimate of the number and the speed of vehicules in major traffic lanes. Follows a prediction procedure that outputs an acoustic pressure level at any location in the modeled area.

Considering as input the acoustic pressure measured in many locations using a sensor grid approach would greatly complement and improve the quality of the predicted pressure values. Among the technical issues that raises this kind of innovative approaches, there is a need to identify which part of the overall acoustic pressure level is due to the road traffic.

In this paper, several techniques based on the non-negative factorization framework are studied in this application scenario. The task being to the best of our knowledge never been considered in the literature, we propose an exprimental protocol to validate the studied approaches that complies with standard reproducible research recommandations.
